### 2022-02-28 unif/unif.tex
unif

>>>>

\blfootnote{In this work I designed the main algorithm, solid oracle and
fingerprint indexing. I also implemented and evaluated the algorithms. Visa
Nummelin proved the completeness of the main algorithm with Alexander Bentkamp's help.
The completeness and termination of solid oracle was proven by me with Alexander
Bentkamp's help.}

\authors{Joint work with\\
Alexander Betnkamp and Visa Nummelin}

\begin{abstract}
  We developed a procedure to enumerate complete sets of higher-order unifiers based on work
  by Jensen and Pietrzykowski. Our procedure removes many redundant unifiers by
  carefully restricting the search space and tightly integrating decision
  procedures for fragments that admit a finite complete set of unifiers. We
  identify a new such fragment and describe a procedure for computing its unifiers.
  Our unification procedure, together with new higher-order term indexing data structures, 
  is implemented in the Zipperposition theorem prover.
  Experimental evaluation shows a clear advantage over Jensen and Pietrzykowski's
  procedure.    
\end{abstract}

\newpage

\section{Introduction}
\label{sec:unif:intro}

\section{Background}
\label{sec:unif:background}

\section{The Unification Procedure}
\label{sec:unif:the-unification-procedure}

\section{Proof of Completeness}
\label{sec:unif:proof-of-completeness}

\section{A New Decidable Fragment}
\label{sec:unif:solid-oracle}

\section{An Extension of Fingerprint Indexing}
\label{sec:unif:indexing}

\section{Implementation}
\label{sec:unif:implementation}

\section{Evaluation}
\label{sec:unif:evaluation}

\section{Discussion and Related Work}

\section{Conclusion}
